cardinalR: Generating interesting high-dimensional data structures

### 2025-04-20 paper-cardinalR.Rmd
Added initial table for cube

>>>>

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube",
                          "gen_cubehole"), 
                      exp = c("",
                              "", 
                              ""))
```

```{r cube-tb-html, eval=is_html_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", col.names = c("Function", "Explanation")) 
```

```{r cube-tb-pdf, eval=is_latex_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
